
\pdfoutput=1

\documentclass[10pt,twocolumn,letterpaper]{article}
%


\usepackage{cvpr}
\usepackage{times}
\usepackage{graphicx,epstopdf}
\usepackage{amsmath,eucal,amssymb}
\usepackage{amssymb,bibspacing,url,xspace}

%
\usepackage[bf,small]{caption}

\usepackage{mdwtab}
\usepackage{multirow}
\usepackage{rotating}

\usepackage[scriptsize]{subfigure}

\usepackage[nospace,compress]{cite}
%



%
%
%

%
%
%
\usepackage{algorithm2e}
%
\let\savedalgorithm\algorithm
\let\savedendalgorithm\endalgorithm
%
\newenvironment{algorithmic}{%
\renewenvironment{algocf}[1][h]{}{}%
\savedalgorithm
}{%
\savedendalgorithm
}
%
%
\let\listofalgorithms\undefined
\usepackage{algorithm}
%

%
\newcommand{\fnorm}[2][2]{\ensuremath{ \left\| #2 \right\|^2_{ \mathrm{#1} } } }
\newcommand\norm[1]{\left\lVert#1\right\rVert}
%
\newcommand{\area}{{\rm area}}
\newcommand{\st}{{{\rm s.t.}\!:}\xspace}
\newcommand{\iid}{{i.i.d.}\xspace}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\newcommand{\trace}{\operatornamewithlimits{Tr}}
\newcommand{\half}{{\frac{1}{2}}}
\newcommand{\quater}{{\frac{1}{4}}}
\newcommand{\crf}{{CRF}\xspace}
\newcommand{\mrf}{{MRF}\xspace}
\newcommand{\cnn}{{CNN}\xspace}


\def\uptext#1{\rotatebox[origin=c]{90}{#1}}


\def\Real{\mathbb{R}}

\def\regress{{z}}
\def\bregress{{\bf z}}
\def\pws{{R}}
\def\bpws{{\bf R}}
%
\def\bd{{\bf 2z}}
\def\x{{\bf x}}
\def\y{{\bf y}}
%
\def\Y{{\bf Y}}
\def\I{{\bf I}}
\def\S{{\bf S}}
\def\D{{\bf D}}
\def\A{{\bf A}}
\def\B{{\bf B}}
\def\J{{\bf J}}
\def\bbeta{{\boldsymbol \beta}}
\def\btheta{{\boldsymbol \theta}}

\def\T{{\mathrm{T}}}
\def\Pr{{\mathrm{Pr}}}

\def\bmu{{\boldsymbol \mu}}
\def\ones{{\boldsymbol  1}}
\def\zeros{{\boldsymbol  0}}
\def\calR{{\cal R}}
\def\calC{{\cal C}}
\def\calN{{\cal N}}
\def\ADot{ { $\bf \cdot$ } }

\def\T{{\!\top}}



\cvprfinalcopy %





\begin{document}



\title{Deep Convolutional Neural Fields for Depth Estimation from a Single Image\thanks{
    This work is in part supported by ARC Grants FT120100969, LP120200485, LP130100156.
    Correspondence should be addressed to C. Shen (email: chhshen@gmail.com).
  }
}


\author{
Fayao Liu$^1$,
Chunhua Shen$^{1,2}$,
Guosheng Lin$^{1,2}$
\\
$^1$The University of Adelaide, Australia
\\
$^2$Australian Centre for Robotic Vision
}


\maketitle






\input{intro.tex}




\input{relatedwork.tex}




\input{method.tex}


\input{exp.tex}


\section{Conclusion}
We have presented a deep convolutional neural field model for depth estimation from a single image.
%
The proposed method combines the strength of deep \cnn and continuous \crf
%
in a unified \cnn framework.
We show that the log-likelihood optimization in our method can be directly solved using back propagation without any approximations required.
Predicting the depths of a new image by solving the MAP inference can be efficiently performed as closed-form solutions exist.
Given the general learning framework of our method, it can also be applied for other vision applications, \eg, image denoising.
%
Experimental results demonstrate that the proposed method outperforms state-of-the-art methods on both indoor and outdoor scene datasets.
%


\appendix

\onecolumn
\input{supp.tex}




\clearpage
{\small
    \bibliographystyle{ieee-cs}
    \bibliography{CaSRef}
}



%
%
%
%
%

\end{document}
